### 2014-08-31 fundamentals/intro.tex
abm section

In order to characterize performance metrics, nuclear fuel cycle analysis 
requires calculation and optimization of myriad physical, nuclear, chemical, 
industrial, and political phenomena. Furthermore, complex systems such as 
nuclear process physics, facility deployment, and material routing each each 
must be modeled simultaneously for even the simplest of nuclear fuel cycle 
simulations.

@@

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to full detail industrial 
models. To date, current tools are either static, fleet-based, or 
privately distributed. An alternative to these approaches is a dynamic, 
agent-based simulator with an open platform.

@@

\gls{ABM} is modern, sophisticated, true to reality, and it takes advantage of modern
computing resources. Furthermore, agent-based modeling provides an analyst a
more natural perspective from which to model a given problem. In the nuclear
fuel cycle context for example, an analyst can design an agent with
reactor-related logic and a separate agent with fuel fabrication-related logic.

>>>>

In order to characterize performance metrics, nuclear fuel cycle analysis 
requires calculation and optimization of myriad physical, nuclear, chemical, 
industrial, and political phenomena. Furthermore, complex systems such as 
nuclear process physics, facility deployment, and material routing each 
must be modeled simultaneously for even the simplest of nuclear fuel cycle 
simulations.

@@

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to high-fidelity industrial 
models. To date, current tools are either static, fleet-based, or 
privately distributed. An alternative to these approaches is a dynamic, 
agent-based simulator with an open platform.

@@

\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it takes advantage of modern computing resources. 
Furthermore, agent-based modeling provides an analyst a more natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context for example, an analyst can design an agent with reactor-related logic 
and a separate agent with fuel fabrication-related logic.
